%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Andreas}{Kvistad}{Computer Science Engineer Student} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Personal}
Andreas Henriksen Kvistad
23. September 1993
Fjellhamar
\section{Contact}
Singsakerbakken 4d, Apartment 22a
7030 Trondheim
~
+47 975 46 336
~
\href{mailto:ahk9339@gmail.com}{ahk9339@gmail.com}
\href{http://facebook.com/andreas.kvistad.9}{fb://andreas.kvistad.9}
\section{Languages}
Norwegian
English fluency
German beginner
\section{Programming}
{\color{red} $\varheartsuit$} Python
Java, C++
HTML
\end{aside}


%----------------------------------------------------------------------------------------
%	MYSELF SECTION
%----------------------------------------------------------------------------------------

\section{Myself}
I am a 24 year old computer science engineer student with a specialization in artificial intelligence. I'm a fast learner, and I like being active in my spare time. I have played football since age six, and I'm currently playing for NTNUi. I chose computer science because I have always been interested in computers, and always enjoyed subjects like math and physics. I grasped programming quickly, as I found it both fun and challenging.


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{2013--2018}
{Masters Degree {\normalfont Computer Science Engineer}}
{Norwegian University of Science and Technology, NTNU}
{\emph{Specialization in Artificial Intelligence} \\ Five-year study of computer science, and a specialization in artificial intelligence after two years. Master thesis about deep learning for NLP, specifically for question answering systems and active learning.}

%------------------------------------------------

\entry
{2016--2017}
{Exchange Student}
{University of California, Santa Barbara}
{Full year abroad in California, Santa Barbara, on my fourth year of studies. Involved a lot of project works, and more social interaction between students and teachers because of the small class sizes.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2012 -- 2013}
{Benterud Skole (Primary School)}
{Benterud Skole, Lørenskog}
{\emph{Teaching Assistant, Daycare worker, Substitute Teacher} \\
Worked at a primary school mainly as a teaching assistant for kids with difficulty in learning, or just helping the teacher out with smaller tasks. I sometimes substituted for teachers in different subjects. Finally, I also worked in the daycare for pupils up to the fourth grade. \\
Experiences:
\begin{itemize}
\item Being patient and creative whilst teaching others
\item Promote good behaviour and generally being a good role model
\item Being professional and honest when interacting with parents and teachers
\end{itemize}}

%------------------------------------------------

\end{entrylist}

\subsection{Part Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2010 -- 2012}
{Losby Gods}
{Losby Gods, Lørenskog}
{\emph{Service Employee} \\
Worked as a waiter in both bigger events as weddings and also \'{a} la carte in the restaurant. Involved a lot of 
interaction with customers and co-workers. \\
Experiences:
\begin{itemize}
\item "The customers always right" - Treating the customer in such a manner
\item Working under a person in charge, respecting orders
\item Still being able to smile after 12 hours at work
\end{itemize}}

%------------------------------------------------


\end{entrylist}

\subsection{Summer Internships}

\begin{entrylist}

\entry
{2016 \& 2017}
{Statnett SF}
{Oslo Nydalen}
{\emph{Summer Intern} \\
Two-part job. Measured grounding in high-voltage tower-pylons, and their capability of leading potentially harmful current away from the tower and safely into the ground. The second part was to plan and draw grounding for new tower areas. This consisted of measuring the relative earth resistivity, and drawing sketches of the area the tower. We then added sufficient grounding to the drawings, according to the measurements we got, along with the general topography of the area. Most of the work were done on-site, on different high-voltage lines around the country.
\\
Responsible for training another team the second year, joining them for a week and supervising their work. 
\\
Experiences:
\begin{itemize}
\item Working in a large-scale company under a leadership
\item Closely work in teams of two, most of the summer
\item Carry out professional work which adhered to the standards of Statnett SF
\item Plan day-to-day work, in order to meet the agenda set by Statnett SF
\end{itemize}}

%------------------------------------------------

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{professional:} Programming, artificial intelligence, deep learning, software development, computer graphics 
\\
\textbf{personal:} Football, guitar, exercise, music, computers

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{References}
\begin{entrylist}

%----------------------------------------------------------------------------------------

\entry
{Statnett SF}
{Arild Kvamme Berstad}
{Oslo, Nydalen}
{\emph{Certificate} written by Arild Kvamme Berstad, Engineer at UTLE - Statnett SF, can be provided upon request.
\\
Contact:
\begin{itemize}
\item +47 909 95 149
\item arild.berstad@statnett.no
\end{itemize}
}


%----------------------------------------------------------------------------------------

\entry
{Benterud}
{Lillian Lauritzen}
{Benterud Skole, Lørenskog}
{\emph{Person of reference}, Lillian Lauritzen, Substitute Teacher Organizer
\\
Contact:
\begin{itemize}
\item +47 977 90 764
\item lillau@lorenskog.kommune.no
\end{itemize}
}

%----------------------------------------------------------------------------------------

\entry
{Losby Gods}
{Heidi Fjellheim}
{Losby Gods, Lørenskog}
{\emph{Person of reference}, Heidi Fjellheim, Director
\\
Contact:
\begin{itemize}
\item +47 970 69 620
\item h.fjellheim@losbygods.no
\end{itemize}
}

\end{entrylist}

%----------------------------------------------------------------------------------------

\end{document}